Demo arXiv template

### 2022-11-23 paper/paper.qmd
pdflatex is happy with \mathbf

---
title: "Demo arXiv template"
format:
  pdf:
    keep-tex: true  
    include-in-header: 
      text: |
        \usepackage{amsmath}
author:
  - name: H. Sherry Zhang
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
    orcid: 0000-0002-7122-1463
    email: huize.zhang@monash.edu
    url: https://huizezhangsh.netlify.app/
  - name: Collaborators
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
abstract: |
  - indexes, useful, quantify severity, early monitoring, 
  - A huge number of indexes have been proposed by domain experts, however, a large majority of them are not being adopted, reused, and compared in research or in practice. 
  - One of the reasons for this is the plenty of indexes are quite complex and there is no obvious easy-to-use implementation to apply them to user's data. 
  - The paper describes a general pipeline framework to construct indexes from spatio-temporal data, 
  - This allows all the indexes to be constructed through a uniform data pipeline and different indexes to vary on the details of each step in the data pipeline and their orders. 
  - The pipeline proposed aim to smooth the workflow of index construction through breaking down the complicated steps proposed by various indexes into small building blocks shared by most of the indexes.
  - The framework will be demonstrated with drought indexes as examples, but appliable in general to environmental indexes constructed from multivariate spatio-temporal data
keywords:
  - indexes
  - data pipeline
  - software design
bibliography: bibliography.bib  
editor_options: 
  chunk_output_type: inline
---

@@

The purpose of normalising is for cross-comparison using the normal score.
This step can get criticism from analysts for ...

This step is usually in the end of the pipeline when the data have been processed into a univariate series. 
When the data are not distributed normally, a distributed is usually fitted before converting to the normal score via the normal reverse CDF function: $\Phi^{-1}(.)$: $\Phi^{-1}[F_{\eta}(x(\mathbf{s}; \mathbf{t}))]$, where $\eta \in H \subseteq \mathbb{R}^{d_{\eta}}$ is the distribution parameter and $d_{\eta}$ is the number of parameter of $\eta$. 
Sometimes, to account for the monthly variation in the data, the fitting is done separately for each month and the noramlising step can be written as $\Phi^{-1}[F_{\eta}^m(x(\mathbf{s};t_{j^*}))]$, where $j^*$ is all the indexes that satisfy $j^* \mod 12 = m$ for each $m = 0, 1,\cdots, 11$.

>>>>

---
title: "Demo arXiv template"
format:
  arxiv-pdf:
    keep-tex: true  
pdf-engine: pdflatex
author:
  - name: H. Sherry Zhang
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
    orcid: 0000-0002-7122-1463
    email: huize.zhang@monash.edu
    url: https://huizezhangsh.netlify.app/
  - name: Collaborators
    affiliations:
      - name: Monash University
        department: Department of Econometrics and Business Statistics
        address: 29 Ancora Imparo Way, Clayton
        city: Melbourne, VIC
        country: Australia
abstract: |
  - indexes, useful, quantify severity, early monitoring, 
  - A huge number of indexes have been proposed by domain experts, however, a large majority of them are not being adopted, reused, and compared in research or in practice. 
  - One of the reasons for this is the plenty of indexes are quite complex and there is no obvious easy-to-use implementation to apply them to user's data. 
  - The paper describes a general pipeline framework to construct indexes from spatio-temporal data, 
  - This allows all the indexes to be constructed through a uniform data pipeline and different indexes to vary on the details of each step in the data pipeline and their orders. 
  - The pipeline proposed aim to smooth the workflow of index construction through breaking down the complicated steps proposed by various indexes into small building blocks shared by most of the indexes.
  - The framework will be demonstrated with drought indexes as examples, but appliable in general to environmental indexes constructed from multivariate spatio-temporal data
keywords:
  - indexes
  - data pipeline
  - software design
bibliography: bibliography.bib  
editor_options: 
  chunk_output_type: inline
---

@@

The purpose of normalising is for cross-comparison using the normal score.
This step can get criticism from analysts for being unnecessarily forcing the scale to the normal scale.
This step is usually in the end of the pipeline when the data have been processed into a univariate series. 
When the data are not distributed normally, a distributed is usually fitted before converting to the normal score via the normal reverse CDF function: $\Phi^{-1}(.)$: $\Phi^{-1}[F_{\eta}(x(\mathbf{s}; \mathbf{t}))]$, where $\eta \in H \subseteq \mathbb{R}^{d_{\eta}}$ is the distribution parameter and $d_{\eta}$ is the number of parameter of $\eta$. 
Sometimes, to account for the monthly variation in the data, the fitting is done separately for each month and the noramlising step can be written as $\Phi^{-1}[F_{\eta}^m(x(\mathbf{s};t_{j^*}))]$, where $j^*$ is all the indexes that satisfy $j^* \mod 12 = m$ for each $m = 0, 1,\cdots, 11$.

### 2022-11-23 paper/paper.tex
pdflatex is happy with \mathbf

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\emph{Discussion: whether we should allow raw data to have different
spatial/ temporal resolution: This would require the notation
\(\symbf{s}\) and \(\symbf{t}\) to depend on \(p\)}

@@

Once variables are collected, they can have different spatial resolution
and temporal granularity. Let \(\symbf{x}(\symbf{s};\symbf{t})\) denote
the raw data that contain the spatial, temporal, and multivariate
aspect: the spatial component
\(\symbf{s} = (s_1, s_2, \cdots, s_n)^\prime\) is defined in the 2D
space: \(\symbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2\), the
temporal component \(\symbf{t} = (t_1, t_2, \cdots, t_J)^\prime\) is
defined in the 1D space:
\(\symbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}\). Expanding on the
multivariate aspect, the data can be written as
\(\symbf{x}(\symbf{s}; \symbf{t}) = (x_1(\symbf{s}; \symbf{t}), x_2(\symbf{s}; \symbf{t}), \cdots, x_P(\symbf{s}; \symbf{t}))^\prime\)

@@

Temporal processing concerns the operations on the temporal aspect of
the data. It can be represented by
\(f_{\mathcal{\psi}}(x(\symbf{s};\symbf{t}))\), where
\(\psi \in \Psi \subseteq \mathbb{R}^{d_{\psi}}\) is the parameters
associated with the temporal operation and \(d_{\psi}\) is the number of
parameter of \(\psi\).

@@

Sometimes, it can be beneficial to borrow information from nearby
spatial locations or there is the need to combine raster data from
satellite images with vector ground measures. Spatial aggregation can be
written as \(g_{\mathcal{\theta}}(x(\symbf{s};\symbf{t}))\), where
\(\theta \in \Theta \subseteq \mathbb{R}^{d_{\theta}}\) is the spatial
operation parameters and \(d_{\theta}\) is the number of parameter of
\(\theta\).

@@

A variable transformation changes the shape of the variable. It can be
written as \(h_{\tau}(x(\symbf{s};\symbf{t}))\), where
\(\tau \in T \subseteq \mathbb{R}^{d_{\tau}}\) is the potential
parameter in the transformation, if any, and \(d_{\tau}\) is the number
of parameter of \(\tau\). Variable transformation involve square root
transformation, log transformation, and also include those non-linear
transformation.

@@

When multiple variables are collected in space and time to construct
indices, they are often summarised with dimension reduction. Dimension
reduction
\(x_{p^*}(\symbf{s}; \symbf{t}) \rightarrow x_p(\symbf{s}; \symbf{t})\),
where \(p^* = 1, 2, \cdots, P^*\), \(p = 1, 2, \cdots, P\), and
\(P^* < P\). The most commonly used dimension reduction
techniquePprincipal Component Analysis (PCA), also called Empirical
Orthogonal Function (EOF), can be written as
\(x_{p^*}(\symbf{s}; \symbf{t}) = \sum_{p = 1}^{P}\lambda_{p}x_p(\symbf{s};\symbf{t})\)
where \(\lambda_p\) is the loading of the PC1, derived from maximising
the variance of the data given the constraint
\(\sum_{p=1}^P\lambda_p^2 = 1\).

@@

The purpose of normalising is for cross-comparison using the normal
score. This step can get criticism from analysts for being unnecessarily
forcing the scale to the normal scale. This step is usually in the end
of the pipeline when the data have been processed into a univariate
series. When the data are not distributed normally, a distributed is
usually fitted before converting to the normal score via the normal
reverse CDF function: \(\Phi^{-1}(.)\):
\(\Phi^{-1}[F_{\eta}(x(\symbf{s}; \symbf{t}))]\), where
\(\eta \in H \subseteq \mathbb{R}^{d_{\eta}}\) is the distribution
parameter and \(d_{\eta}\) is the number of parameter of \(\eta\).
Sometimes, to account for the monthly variation in the data, the fitting
is done separately for each month and the noramlising step can be
written as \(\Phi^{-1}[F_{\eta}^m(x(\symbf{s};t_{j^*}))]\), where
\(j^*\) is all the indexes that satisfy \(j^* \mod 12 = m\) for each
\(m = 0, 1,\cdots, 11\).

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, breakable, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced]}{\end{tcolorbox}}\fi

@@

\emph{Discussion: whether we should allow raw data to have different
spatial/ temporal resolution: This would require the notation
\(\mathbf{s}\) and \(\mathbf{t}\) to depend on \(p\)}

@@

Once variables are collected, they can have different spatial resolution
and temporal granularity. Let \(\mathbf{x}(\mathbf{s};\mathbf{t})\)
denote the raw data that contain the spatial, temporal, and multivariate
aspect: the spatial component
\(\mathbf{s} = (s_1, s_2, \cdots, s_n)^\prime\) is defined in the 2D
space: \(\mathbf{s} \in \mathcal{D}_s \subseteq \mathbb{R}^2\), the
temporal component \(\mathbf{t} = (t_1, t_2, \cdots, t_J)^\prime\) is
defined in the 1D space:
\(\mathbf{t} \in \mathcal{D}_t \subseteq \mathbb{R}\). Expanding on the
multivariate aspect, the data can be written as
\(\mathbf{x}(\mathbf{s}; \mathbf{t}) = (x_1(\mathbf{s}; \mathbf{t}), x_2(\mathbf{s}; \mathbf{t}), \cdots, x_P(\mathbf{s}; \mathbf{t}))^\prime\)

@@

Temporal processing concerns the operations on the temporal aspect of
the data. It can be represented by
\(f_{\mathcal{\psi}}(x(\mathbf{s};\mathbf{t}))\), where
\(\psi \in \Psi \subseteq \mathbb{R}^{d_{\psi}}\) is the parameters
associated with the temporal operation and \(d_{\psi}\) is the number of
parameter of \(\psi\).

@@

Sometimes, it can be beneficial to borrow information from nearby
spatial locations or there is the need to combine raster data from
satellite images with vector ground measures. Spatial aggregation can be
written as \(g_{\mathcal{\theta}}(x(\mathbf{s};\mathbf{t}))\), where
\(\theta \in \Theta \subseteq \mathbb{R}^{d_{\theta}}\) is the spatial
operation parameters and \(d_{\theta}\) is the number of parameter of
\(\theta\).

@@

A variable transformation changes the shape of the variable. It can be
written as \(h_{\tau}(x(\mathbf{s};\mathbf{t}))\), where
\(\tau \in T \subseteq \mathbb{R}^{d_{\tau}}\) is the potential
parameter in the transformation, if any, and \(d_{\tau}\) is the number
of parameter of \(\tau\). Variable transformation involve square root
transformation, log transformation, and also include those non-linear
transformation.

@@

When multiple variables are collected in space and time to construct
indices, they are often summarised with dimension reduction. Dimension
reduction
\(x_{p^*}(\mathbf{s}; \mathbf{t}) \rightarrow x_p(\mathbf{s}; \mathbf{t})\),
where \(p^* = 1, 2, \cdots, P^*\), \(p = 1, 2, \cdots, P\), and
\(P^* < P\). The most commonly used dimension reduction
techniquePprincipal Component Analysis (PCA), also called Empirical
Orthogonal Function (EOF), can be written as
\(x_{p^*}(\mathbf{s}; \mathbf{t}) = \sum_{p = 1}^{P}\lambda_{p}x_p(\mathbf{s};\mathbf{t})\)
where \(\lambda_p\) is the loading of the PC1, derived from maximising
the variance of the data given the constraint
\(\sum_{p=1}^P\lambda_p^2 = 1\).

@@

The purpose of normalising is for cross-comparison using the normal
score. This step can get criticism from analysts for being unnecessarily
forcing the scale to the normal scale. This step is usually in the end
of the pipeline when the data have been processed into a univariate
series. When the data are not distributed normally, a distributed is
usually fitted before converting to the normal score via the normal
reverse CDF function: \(\Phi^{-1}(.)\):
\(\Phi^{-1}[F_{\eta}(x(\mathbf{s}; \mathbf{t}))]\), where
\(\eta \in H \subseteq \mathbb{R}^{d_{\eta}}\) is the distribution
parameter and \(d_{\eta}\) is the number of parameter of \(\eta\).
Sometimes, to account for the monthly variation in the data, the fitting
is done separately for each month and the noramlising step can be
written as \(\Phi^{-1}[F_{\eta}^m(x(\mathbf{s};t_{j^*}))]\), where
\(j^*\) is all the indexes that satisfy \(j^* \mod 12 = m\) for each
\(m = 0, 1,\cdots, 11\).
